The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-14 Paper_third_version/Article_UV_Mexico.tex
Figures 6 and 7 with the same size
Chnage on Table 4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 40\% in
  2000 and 25\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite- and ground-based UVI, and showed specific
  contributions from aerosols in the boundary layer and the free troposphere,
  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
  decreasing order of importance. Such large changes in UV radiation
  between 2000 and 2019 have important implications ranging from human
  health (skin cancer and cataract induction) to air pollution control
  (photochemical smog formation).
\end{abstract}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/CSUVindex}
    \caption{{UV Index at solar noon for clear sky recorded by OMI-Aura/NIVR-FMI-NASA,
          from 2005 to 2019.
            {\label{485116}}%
        }}
  \end{center}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{June-July}                              & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
        observations (OMI), and modeled for different pollution levels (TUV).
      }}
  \label{table:TUVmodel}
\end{table}

@@

Table~{\ref{table:year2000-2019}} shows the contribution of different pollutants
to the UVI increase between 2000 and 2019, computed with the TUV model.
The year 2000 was taken as the base case, and each pollutant was decreased
to its 2019 value individually while the others were maintained at their 2000 value.
Decreasing aerosol AOD has been the largest driver of the UVI changes,
but the absorption by gaseous pollutants has also decreased significantly.
Additional future reductions in AOD, NO\textsubscript{2}, and O\textsubscript{3} could increase the
UVI further, while the low SO\textsubscript{2} levels reached by 2019 are expected
to have negligible effects in the UVI.

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/jvals}
    \caption{{Vertical profiles of the photolysis coefficients for the
          reaction~\(O_3 + h\nu \rightarrow O(1D) + O_2\) (top axis, blue)~\(NO_2 + h\nu \rightarrow O+NO \) (bottom
          axis, red) for zero pollution (solid) and Mexico City in the years 2000
          (dashed) and 2019 (dotted)
          {\label{973680}}%
        }}
  \end{center}
\end{figure}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{cc}
    \hline
    Pollutant           & UVI Change \\ \hline
    AOD                 & 0.8        \\
    O\textsubscript{3}  & 0.4        \\
    NO\textsubscript{2} & 0.4        \\
    SO\textsubscript{2} & 0.5        \\ \hline
  \end{tabular}
  \caption{Contributions of individual pollutants to the 2000-2019 UV Index changes. Baseline calculation for 2000 conditions (AOD = 0.7, O\textsubscript{3} = 70 ppb, NO\textsubscript{2} = 40 ppb, SO\textsubscript{2} = 20 ppb). Individual pollutant contributions are estimated by adjusting each pollutant, one at the time, to its 2019 value (AOD = 0.5, O\textsubscript{3} = 50 ppb, NO\textsubscript{2} = 20 ppb, SO\textsubscript{2} = 1 ppb), while maintaining the others at their 2000 value.}
  \label{table:year2000-2019}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 40\% in
  2000 and 25\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite and ground-based UVI, and showed specific contributions
  from aerosols, O\textsubscript{3}, NO\textsubscript{2},
  and SO\textsubscript{2}, in decreasing order of importance. Such large
  changes in UV radiation between 2000 and 2019 have important implications
  ranging from human health (skin cancer and cataract induction) to air
  pollution control (photochemical smog formation).
\end{abstract}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.95\columnwidth]{figures/CSUVindex}
    \caption{{UV Index at solar noon for clear sky recorded by OMI-Aura/NIVR-FMI-NASA,
          from 2005 to 2019.
            {\label{485116}}%
        }}
  \end{center}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.95\columnwidth]{figures/Monthly_mean_RD.png}
  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{June-July}                              & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
        observations (OMI), and modeled for different pollution levels (TUV calculation for 21 June at solar noon).
      }}
  \label{table:TUVmodel}
\end{table}

@@

Table~{\ref{table:year2000-2019}} shows the contribution to UVI reductions from individual pollutants,
computed with the TUV model for conditions similar to those in Table {\ref{table:TUVmodel}} (21 June solar noon).
If the pollutant levels of the year 2000 are added one at the time to a pollution-free atmosphere
(see middle column of Table {\ref{table:year2000-2019}}),
aerosols account for more than half of the total UVI reduction,
with the gases O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2},
contributing in order of importance to the remainder. It should be noted that the sum
of these individual contributions (-6.8) differs from the value obtained if these pollutants
are applied simultaneously rather than one at the time (-5.9, from Table {\ref{table:TUVmodel}}).
This non-additivity results mainly from (1) saturation of overlapping absorption spectra,
especially for O\textsubscript{3} and SO\textsubscript{2} at the shortest wavelengths, and (2)
interactions between absorption and scattering, e.g. aerosols causing a change in photon
pathlengths through absorbing gases; both effects are treated in the TUV model.

The right column of Table {\ref{table:year2000-2019}} shows the contribution of the individual pollutants to the UVI
increase experienced over the years 2000-2019. For this calculation, the pollutants
were decreased individually to their 2019 level while the others were held at the 2000 values.
Aerosol reductions were the largest single factor responsible for the UV increase,
but more than half of the increase was due to reductions of the gases, of which the near-complete
elimination of SO\textsubscript{2} was most important. The total increase computed from the sum (1.8) is in
good agreement with the 2000-2019 increase in which all pollutants were changed simultaneously
(1.9, from Table {\ref{table:TUVmodel}}), as smaller changes in UVI mitigate non-linearities.

\begin{table}[H]
  \centering
  \begin{tabular}{lcc}
    \hline
    Pollutant           & $\Delta$UVI, 2000 - zero pollution (a) & $\Delta$UVI, 2000-2019 (b) \\ \hline
    AOD                 & -3.7                                   & 0.8                        \\
    O\textsubscript{3}  & -1.4                                   & 0.3                        \\
    NO\textsubscript{2} & -0.9                                   & 0.3                        \\
    SO\textsubscript{2} & -0.8                                   & 0.4                        \\
    \textbf{Total}      & \textbf{-6.8}                          & \textbf{1.8}               \\\hline
  \end{tabular}
  \caption{Contribution of different pollutants to UV Index changes in Mexico City, calculated with the TUV model for 21 June at solar noon. (a) Pollutants from year 2000 added to clean atmosphere, one at the time. (b) Pollutants lowered from 2000 to 2019 levels, one at the time.}
  \label{table:year2000-2019}
\end{table}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/jvals}
    \caption{{Vertical profiles of the photolysis coefficients for the
          reaction~\(O_3 + h\nu \rightarrow O(1D) + O_2\) (top axis, blue)~\(NO_2 + h\nu \rightarrow O+NO \) (bottom
          axis, red) for zero pollution (solid) and Mexico City in the years 2000
          (dashed) and 2019 (dotted). TUV calculation for 21 June at solar noon.
            {\label{973680}}%
        }}
  \end{center}
\end{figure}

@@
